# Bidar




```{r echo=FALSE,warning=FALSE, message=FALSE,  results='hide'}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = F)

library(simplevis)
library(dplyr)
library(sf)
library(ggplot2)
library(magrittr)

```

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
library(magrittr)
kal_polygon <- sf::st_read("/Volumes/Macintosh HD - Data/Users/srirama/Documents/raviuitp/bidar_division/wgs_bidar_accessibility.shp") 
kal_polygon <- kal_polygon %>% select(-c(LGDGPCode)) %>% mutate(accessibility = cut(NUMPOINTS, breaks=c(-Inf,0,1,2,5,10,Inf)))
kal_boundary <- kal_polygon %>% group_by(created_us) %>% summarise() 

cities <-   read.csv("/Users/srirama/github_projects/ksrtc/data/cities.csv") %>% 
  select(Worksheet, Depot, long, lat)
city_sf <- st_as_sf(x = cities,                         
           coords = c("long", "lat"),
           crs = "EPSG:4326")

kal_routes <- read_sf("/Volumes/Macintosh HD - Data/Users/srirama/Documents/raviuitp/bidar_division/bidar_division.shp")

state_boundary <- read_sf("/Volumes/Macintosh HD - Data/Users/srirama/Documents/raviuitp/shapefiles/State/State_Boundary.shp")


```


-   In total `r nrow(kal_routes)` trips were mapped for Bidar
-   These trips cover about `r 100 - as.integer((kal_polygon %>% filter(NUMPOINTS ==0) %>% nrow())/nrow(kal_polygon) * 100)` percent of villages in the district.
-   A total of `r kal_polygon %>% filter(NUMPOINTS ==0) %>% nrow()` villages are not covered by any bus service.
-   The spatial distribution of trips are shown in figure \@ref(fig:routesBid)
-   The spatial distribution of villages covered and villages not covered by the bus services are shown in figure \@ref(fig:accessBid)

```{r routesBid, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.cap = "Extent of services from Bidar"}
# Get the rectangular bounding box



ggmap(mad_map) + 
  geom_sf(data=kal_routes, inherit.aes = F, size = 0.4, col = "#165430") +
  geom_sf(data= state_boundary, fill = NA, col = "red", inherit.aes = F)+
  theme(axis.title=element_blank())

```

```{r accessBid, echo = FALSE, fig.cap = "Accessibility in Bidar"}

library(RColorBrewer)
brk<-levels(kal_polygon$accessibility)
colr <- c("red", "blue", "green", "yellow", "pink", "lightgray")
labls <- c("No service", "1 per day", "2 per day", "3-5 per day", "5-10 per day", "more than 10 per day")
colrr <- c("red", rev(brewer.pal(5, "Greens")))



ggplot(kal_polygon ) + geom_sf(aes(fill = accessibility),col = "NA") +
  scale_fill_manual(values = colrr, breaks = brk, labels = labls )+
  theme_bw()+
  geom_sf(data= city_sf %>% filter(Worksheet == "Bidar")) +
  geom_text(data= cities %>% filter(Worksheet == "Bidar"), aes(x= long, y = lat, label = Depot), vjust=-1)+
  theme(axis.title=element_blank())
  

```

